Associations_PFN_Cognition

### 2022-09-12 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
subject ID fix
added line 46 to fix the subject ID names (NDARINV vs. NDAR_INV)

# First load in the spatial extent of each PFN (they're in order, 1-17)
```{r}
pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv") # n=9,132
# Change PFN column names so they're sensible
colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
```

>>>>

# First load in the spatial extent of each PFN (they're in order, 1-17)
```{r}
pfn_sizes <- read.csv("/Users/askeller/Documents/Kellernet_PrelimAnalysis/All_PFN_sizes.csv") # n=9,132
# Change PFN column names so they're sensible
colnames(pfn_sizes)<-c("subjectkey","PFN1","PFN2","PFN3","PFN4","PFN5","PFN6","PFN7","PFN8","PFN9","PFN10","PFN11","PFN12","PFN13","PFN14","PFN15","PFN16","PFN17")
pfn_sizes$subjectkey<-gsub('sub-NDARINV','NDAR_INV',pfn_sizes$subjectkey)
```
